---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body{
font-size:20px;
color: #000000;
background-color: #f0f0f0;
font-family: "Arial";
}
h1{
text-align: center;
}
h2{
color: #ff6600
}

```

# **BALANCING STUDENT LIFE**

## This is what some starting observation of collected data looks like:

```{r}
library(tidyverse)
library(knitr)

logged_data = read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQP_1fNXabj84D3fZOPSbYNXECUpItLPvQWX99VvGOaPo6bxwbVtnzsDtOTLT2Gl2LBKCJ9HNGlC4hc/pub?gid=890585265&single=true&output=csv")

logged_data <- logged_data %>% select(-`Score`)
#view(logged_data)

latest_data <- logged_data %>% rename(Sleep_Duration = 2, Physical_Activity_Status = 3, Study_Duration = 4, Number_of_Meals = 5, Number_of_Classes = 6)
#view(latest_data)

kable(head(latest_data))

#glimpse(latest_data)
```
## The below given are some summary stastics for the data that I found would be useful were:

```{r}
maximum_hours_studied = max(latest_data$Study_Duration)
print(paste("The maximum number of hours an individual studied from the data collected was :", maximum_hours_studied))

average_number_of_classes <- mean(latest_data$Number_of_Classes, na.rm = TRUE)
print(paste("The average number(rounded up) of classes each day for students who participated in the study is:", ceiling(average_number_of_classes)))

sleep_duration <- max(latest_data$Sleep_Duration)
print(paste("The maximum number of students from this data collected usually sleep for",sleep_duration))
```

## DATA VISUALIZATION

**The below bar chart shows the frequency of students in collected data who have a physical activity in their life fall in the category they sleep more or less.**

```{r}
sleep_activity_plot <- ggplot(data=latest_data) +
  geom_bar(aes(x = Physical_Activity_Status, fill = Sleep_Duration)) +
  scale_fill_manual(values = c("#ff007f","Purple","#004EFF")) +
  labs(title = "Does good Sleep implies being Energetic ", 
       subtitle = "Bar Chart for comparing how physical activitives are hindered by sleep duration.",
       x = " Physical Activity ",
       y = " Number of People "
       )

print(sleep_activity_plot)

```

**The below bar chart shows the frequency of students in collected data if student have had more meals in a day tend to study for fall in the category of who study more study.**


```{r}
study_meals_plot <- latest_data %>% ggplot() +
  geom_bar(aes(x = Study_Duration, fill = Number_of_Meals)) +
  scale_fill_manual(values = c("SkyBlue", "Orange", "DarkGreen","Yellow"))+
  scale_x_continuous(breaks = seq(0,24, by = 1)) +
  labs(title = "Does more Meals implies more Study Time" , 
       subtitle = "Bar chart to compare if more meals helps people study for longer time.",
       x = " Duration of Study time ",
       y = " Frequency of people with same study time ")

print(study_meals_plot)
```